### 2020-02-06 paper/revisions/review-responses.tex

               Moreover, we rewrite the paragraph in page 11 to address this thought:\\
               \begin{enumerate}
               	\item The simulation starts without injecting refueling materials (i.e. only removing FPs and Pa).
               	\item After the first depletion calculation step, we check the total mass density of FPs and Pa in the \texttt{FP-waste tank} and \texttt{Pa-decay tank}, respectively.
               	\item A simple calculation yields the amount of heavy metal that must be added during this cycle:
               	\subitem 3a. \textbf{Thorium feed mechanism}: mass of injected $^{233}$U $\approx$ mass of extracted Pa and mass of injected Th $\approx$ mass of extracted FPs to maintain the total fuel mass constant.
               	\subitem 3b. \textbf{Non-thorium feed mechanism}: mass of injected $^{233}$U $\approx$ mass of extracted Pa and mass of injected fuel (i.e., HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) $\approx$ mass of extracted FPs to maintain the total fuel mass constant.
               	\item Dividing this mass by time and inventory of refueling material gives the corresponding feed constant (1/s).
               \end{enumerate}
               In both feed mechanisms (thorium and non-thorium) we continuously added $^{233}$U and the mass of injected $^{233}$U is equal to the mass of extracted Pa ($^{233}$Pa decays to $^{233}$U after $\approx$ 27 d). To keep the total fuel mass almost constant, for \textbf{thorium feed mechanism}, the mass of injected Th must be equal to the mass of extracted FPs and for \textbf{non-thorium feed mechanism}, the mass of injected fuel (i.e., HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) must be equal to the mass of extracted FPs.

        \end{solution}

        %--------------------------------------------------------------------

        \question Phenomenons presented in Figure 3 that K-eff for the case of Pu+HALEU firstly increases and then decreases, and the time to become subcritical for the case of reactor-grade Pu is longest (except the case of U-233) should be explained.
        \begin{solution}
                 Thank you for your insightful comment. Phenomenons presented in Figure 3 have been described in the manuscript.

                 The following paragraph has been added to the manuscript.\\
                 For Pu+HALEU case, K${_eff}$ firstly increases during the first $\approx$ $3$ EFPY and after that decreases. This is due to the conversion of $^{238}$U from HALEU into fissile plutonium, which often produces the majority of the fission power until the transition to Th/$^{233}$U fuel cycle. Figure~\ref{fig:diffPuAll811} shows the variation of fissile plutonium isotopes ($^{239}$Pu , $^{241}$Pu, and $^{243}$Pu) during reactor operation. For TRU and reactor-grade Pu, the fissile plutonium isotopes are depleted, during operating (the fissile material is dominated by Pu in these cases). For HALEU case, the fissile material is dominated by $^{235}$U, however, $^{238}$U is converted into fissile plutonium. Therefore, the mass of fissile plutonium increases during operating but its value still relatively low. For Pu+HALEU case, the mass of the fissile plutonium isotopes increases within the first $\approx$ 3 EFPY and then decreases. The reactivity from the produced Pu is much greater than the depletion of the initial reactivity (due to the depletion of initial fissile isotopes), consequently, K${_eff}$ increases during the first $\approx$ 3 years and then decreases; the amount of $^{233}$U generated in the Pu+HALEU case is insufficient to maintain the reactor criticality and counteract neutron absorption in non-fissile isotopes.

                 The following paragraph has been added to the manuscript.\\
                 Figure~\ref{fig:keff1} shows that the decrease in K${_eff}$ for reactor-grade Pu case occurs at a much later operating time than for other cases, this is because of the neutron spectrum in the reactor-grade Pu initial core is hardened; more $^{232}$Th is being converted to $^{233}$U. Nevertheless, this amount of the $^{233}$U is not enough to counteract the neutron absorption in the non-fissile Pu isotopes after much of the $^{239}$Pu and $^{241}$Pu is depleted.

### 2020-02-06 paper/results.tex
Comments from Reviewer 2 (4)

Notably, the molar fractions of \gls{HALEU} and reactor-grade Pu in the initial fuel composition were increased
more. Consequently, the initial $k_{eff}$ for these cases increased (Figure~\ref{fig:keff1} (HALEU and reactor-grade Pu cases)).
For the HALEU fuel salt, the amount of $^{233}$U generated in the SD-TMSR after a few years is insufficient to counteract the absorption of the (non-fissile) $^{238}$U added at start-up after much of the original $^{235}$U is depleted. Consequently, the core becomes subcritical after $\approx$ $6$ years of operation.
For the reactor-grade Pu fuel salt, the core becomes subcritical after $\approx$ $12$ years because the amount of $^{233}$U generated is not sufficient to counteract the neutron absorption in the non-fissile plutonium isotopes after much of the $^{239}$Pu and $^{241}$Pu is depleted \cite{betzler2016modeling}.

>>>>

Notably, the molar fractions of \gls{HALEU} and reactor-grade Pu in the initial fuel composition were increased
more. Consequently, the initial $k_{eff}$ for these cases increased (Figure~\ref{fig:keff1} (HALEU and reactor-grade Pu cases)).
For the HALEU fuel salt, the amount of $^{233}$U generated in the SD-TMSR after a few years is insufficient to counteract the absorption of the (non-fissile) $^{238}$U added at start-up after much of the original $^{235}$U is depleted. Consequently, the core becomes subcritical after $\approx$ $6$ years of operation.

For Pu+HALEU case, K${_eff}$ firstly increases during the first $\approx$ $3$ EFPY and after that decreases. This is due to the conversion of $^{238}$U from HALEU into fissile plutonium, which often produces the majority of the fission power until the transition to Th/$^{233}$U fuel cycle. Figure~\ref{fig:diffPuAll811} shows the variation of fissile plutonium isotopes ($^{239}$Pu , $^{241}$Pu, and $^{243}$Pu) during reactor operation. For TRU and reactor-grade Pu, the fissile plutonium isotopes are depleted, during operating (the fissile material is dominated by Pu in these cases). For HALEU case, the fissile material is dominated by $^{235}$U, however, $^{238}$U is converted into fissile plutonium. Therefore, the mass of fissile plutonium increases during operating but its value still relatively low. For Pu+HALEU case, the mass of the fissile plutonium isotopes increases within the first $\approx$ 3 EFPY and then decreases. The reactivity from the produced Pu is much greater than the depletion of the initial reactivity (due to the depletion of initial fissile isotopes), consequently, K${_eff}$ increases during the first $\approx$ 3 years and then decreases; the amount of $^{233}$U generated in the Pu+HALEU case is insufficient to maintain the reactor criticality and counteract neutron absorption in non-fissile isotopes.

Figure~\ref{fig:keff1} shows that the decrease in K${_eff}$ for reactor-grade Pu case occurs at a much later operating time than for other cases, this is because of the neutron spectrum in the reactor-grade Pu initial core is hardened; more $^{232}$Th is being converted to $^{233}$U. Nevertheless, this amount of the $^{233}$U is not enough to counteract the neutron absorption in the non-fissile Pu isotopes after much of the $^{239}$Pu and $^{241}$Pu is depleted \cite{betzler2016modeling}.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{diffPuAll811.png}
		\vspace{-0.5in}
	\caption{The variation of relative mass of fissile Pu ($^{239}$Pu , $^{241}$Pu, and $^{243}$Pu) during reactor operation.} 
	\label{fig:diffPuAll811}
\end{figure}
